% ===========================================
% HOMEWORK 1: Variables and Sensors
% Written by: Braidan Duffy
%
% Date: 01/05/2023
% Last Revision: 01/05/2023
% ============================================

\documentclass[
	letterpaper, % Page size
	fontsize=10pt, % Base font size
	twoside=true, % Use different layouts for even and odd pages (in particular, if twoside=true, the margin column will be always on the outside)
	%open=any, % If twoside=true, uncomment this to force new chapters to start on any page, not only on right (odd) pages
	%chapterentrydots=true, % Uncomment to output dots from the chapter name to the page number in the table of contents
	numbers=noenddot, % Comment to output dots after chapter numbers; the most common values for this option are: enddot, noenddot and auto (see the KOMAScript documentation for an in-depth explanation)
]{kaobook}

\usepackage{pdfpages}
\usepackage{array}

\begin{document}

\pagelayout{wide} % Remove margin

\chapter*{Homework 1: Variables and Sensors}

\section*{Overview}
For this assingnment, you will \textbf{\emph{individually}} brainstorm and create three lists.

\begin{enumerate}
	\item Relevant variables related to the motion of a surfer on a wave. 
	As you create this list include how you might collect the data for each variable you have listed.
	\item Relevant variables related to wave dynamics. 
	As you create this list include how you might collect the data for each variable you have listed.
	\item How many ways can you think of to combine variables from each of the above 2 lists? 
	List those variable combinations and include the relevant physical connection you are thinking you can capture. 
\end{enumerate}

\section*{Requirements}
The first two lists should have at least 5 variables on them and a decent number of sensors to accompany them.
Do \emph{not} consider what the class has access to while creating these lists, just name anything and everything that comes to mind.

\section*{Grading}
This assignment will use a pass-fail scheme.
If your lists of variables is deemed not sufficient by the instructor, you will receive a 0 with the option to redo.
Otherwise, you will receive full credit.

\end{document}